% Added by Joe
As most of the components in this product are Commercial Off The Shelf (COTS) components, a repository of relevant documentations will be curated to help a maintainer troubleshoot issues that may arise. As this project largely depends on third-party software with specific version constraints, it is important that software version requirements are specified in adherence to REP and PEP protocols. This helps ensure that the product continues to work when the software is re-installed or migrated to a new computer. In the case major hardware components fail they will need to be serviced by an authorized repair center or repurchased if outside warranty/support period. 

%Include a header paragraph specific to your product here. Maintenance and support requirements address items specific to the ongoing maintenance and support of your product after delivery. Think of these requirements as if you were the ones who would be responsible for caring for customers/end user after the product is delivered in its final form and in use "in the field". What would you require to do this job? Specify items such as: where, how and who must be able to maintain the product to correct errors, hardware failures, etc.; required support/troubleshooting manuals/guides; availability/documentation of source code; related technical documentation that must be available for maintainers; specific/unique tools required for maintenance; specific software/environment required for maintenance; etc.

%\subsection{Requirement Name}
%\subsubsection{Description}
%Detailed requirement description...
%\subsubsection{Source}
%Source
%\subsubsection{Constraints}
%Detailed description of applicable constraints...
%\subsubsection{Standards}
%List of applicable standards
%\subsubsection{Priority}
%Priority

\subsection{Third Party Software Documentation}
\subsubsection{Description}
In order to make maintaining the software involved with the UR5 Jenga-Playing Robot, we shall compile documentation for the software packages that we use.
\subsubsection{Source}
Gabriel Comer
\subsubsection{Constraints}
We will only be able to compile documentation that already exists. There isn't an expectation to write documentation for COTS products.
\subsubsection{Standards}
N/A
\subsubsection{Priority}
Medium

\subsection{Legacy Communications}
\subsubsection{Description}
We will maintain communication with customers who choose to keep supporting the product. If any problems arise with the product after full delivery, depending on availability we will assist in patching or resolving the issue.
\subsubsection{Source}
Maxwell Sanders
\subsubsection{Constraints}
Theses communications will only last as long as the product support and will also be constrained to our personal time after graduation.
\subsubsection{Standards}
N/A
\subsubsection{Priority}
Future