This section contains the approximate budget for the project, where that money will come from, and any other support. This text should be replaced with a discussion and justification of major expenses, but not the actual monetary amounts (that will go in the preliminary budget section below). 
\begin{itemize}
    \item \textbf{Gripper}: One of the pivotal parts of the project is giving the robot the ability to actually interact with the tower. A proper gripper is worth the cost, since it is our only way for the robot to interact.
    
    \item \textbf{Camera}: The other pivotal part of the project. This gives our robot the ability to scan and analyze the tower. A Camera is necessary since without it the robot would be incapable of dynamic play.

    \item \textbf{Custom Jenga Tower}: A jenga tower that works for our project will likely have to be custom made. We would like to 3D print a tower ourselves so that we have control over the tower's specifications, which would be great since 3D printing would come at negligible cost to us. We would like to make slightly larger than usual blocks, with markings to easily distinguish the short and long sides of each block. The cost of a custom jenga tower should be less than \$100.
\end{itemize}
\subsection{Preliminary Budget}
\begin{table}[h!]
	\centering
	\begin{tabular}{|l|l|r|r|}
		\hline
		Category    &  Item                   & Quantity & Budget     \\
		\hline
        Gripper     & Robotiq Finger          &   1      & \$0-\$3000 \\
		Camera      & Intel Realsense / C9P   &   1      & \$0-\$150  \\
		Robot       & UR5                     &   1      & \$0        \\
  		Computer    & Intel NUC / NVIDIA TX2  &   1      & \$600      \\
  		Jenga Set   & Jumbo Jenga Extreme     &   1      & \$100      \\
  		IO          & Monitor                 &   1      & \$0-\$100  \\
  		            & KB/ USB Buttons         &   2      & \$0-\$10   \\
		\hline
	\end{tabular}
\end{table}

\subsection{Current \& Pending Support}
\begin{itemize}
    \item \textbf{CSE Department}: \$800 This is the default funding given to every Senior Design Project.
    \item \textbf{Cloud9 Perception}: \$? Dr. McMurrough has expressed interest in supporting this for trade show demonstrations.
\end{itemize}
